---
title: "anova-in-r"
author: "Alton Lu"
date: "June 17, 2019"
output: 
  html_document:
    toc: true
    toc_depth: 2
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Anova in R {.tabset}

ANOVA (analysis of variance)
- An extension of t-tests where there are more than 2 groups. Grouping is doen through a factor variable.



Key Assumptions:
- Observations are independent and randomly sampled from the population of each group
- Data in each group are normally distributed
- The normal populations have a common variance (Leverne's Test)


Two Types of Anova:
- One Way Anova
  - Hypothesis:
    - Null: the means are the same between all groups
    - Alternative: the means of at least one group are different
- Two Way Anova
  - Hypothesis:
    - Null: the means are the same between all groups, there is no interaction between the two groups
    
    - Alternative: the means of at least one group are different, there is an interaction between groups 


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
