---
title: "writing-functions-in-r"
author: "Alton Lu"
date: "March 27, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Breaking down a function

In R Programming:
1. Everything that exists is an object. Dataframe, vector, variables - all objects.
2. Everything that happens is a function call

When you use max(x), max() is a function call. By calling max(), something happens to x, which is an object. min(x) is a function call of min() that finds the minimum value in x.


```{r data}
x1 <- c(1, 2, 3, 4, 5, 20)
x2 <- c(3, -20, 4, 5, 6, 10)
```

## Find the min and the max of x1 and x2

```{r}
min(x1)
max(x1)
min(x2)
max(x2)
```

## Write a function min_max() that can produce the following output:
  - "The Minimum of the data is x"
  - "The Maximum of the data is x"
  

```{r}
min_max <- function(data, find_max){
  if (find_max == 1){
    a = paste("The maximum of the data is", max(data))
    
    print(a)
  } else if (find_max == 0){
    a = paste("The minimum of the data is", min(data))
    
    print(a)
  }
}


min_max(x1, find_max=1)

```

## Write a function called custom_max() that finds the max of a vector without using the max() function. Your custom_max fucntion should return:
  - 20 for x1
  - 10 for x2

```{r}
custom_max <- function(values){
    a = values[1]
  for(i in values){
    if(i > a){
      a = i
    }
  }
  
  return(a)
}

custom_max(x2)
```

## We now have new data with NA's. Modify your custom_max function to find the max even if there are NA's. 

```{r}
x1 <- c(1, 2, 3, 4, NA, 5, 20, NA)
x2 <- c(3, -20, NA, 4, 5, 6, 10, NA)
```








