---
title: "writing-functions-solutions"
author: "Alton Lu"
date: "March 27, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Breaking down a function

In R Programming:

1. Everything that exists is an object. Dataframe, vector, variables are all objects.

2. Everything that happens or does something is a function call.

When you use max(x), max() is a function call. By calling max(), something happens to the object x.

Every function is made of three parts:

  1. Input. Also called arguments or formals. For the max() function, this would just be a vector of numbers as input. 
  2. Body. This is whatever the function does. The max() function finds the largest number.
  3. Output. Also called a return value. 



```{r data}
# Do not change this code
x1 <- c(1, 2, 3, 4, 5, 20)
x2 <- c(3, -20, 4, 5, 6, 10)
```

## 2. Find mins and maxes

Find the min and max of the vector x1

```{r}
min(x1)
max(x1)
```

## 3. Write a function 


Write a function min_max() that can print either of following:

  - "The minimum of the data is x"
  - "The maximum of the data is x"

Function inputs:

  1. A vector of numbers (x1 or x2)
  2. A way of specifying if you want to find the min or the max

Output:

  1. If you want the max, the function should print: "The maximum of the data is x"
  2. If you want the min, the function should print: "The minimum of the data is x"
  

```{r}
min_max <- function(data, find_max){
  if (find_max == 1){
    a = paste("The maximum of the data is", max(data))
    
    print(a)
  } 
  else if (find_max == 0){
    a = paste("The minimum of the data is", min(data))
    
    print(a)
  }
}

min_max(x1, find_max=1)

```

## 4. Write a custom max function

Write a function called custom_max() that finds the max of a vector without using the max() function. 

Inputs:

  - A single vector of numbers
  
Outputs:

  - 20 if using vector x1
  - 10 if using vector x2


```{r}
custom_max <- function(values){
  a = values[1]
  for(i in values){
    if(i > a){
      a = i
    }
  }
  
  return(a)
}

custom_max(x2)
```


## 5. Create Test Data

Create a function test_split() that creates a test set of a dataframe.

Inputs:

  1. Dataframe or matrix
  2. p parameter that specifies the proportion of the data considered the test set. This should be a number between 0 and 1. p=.5 means that 50% of the data will be considered the test set

Output:

  1. A dataframe of size p*nrow(data) that can be used as a test data set

Notes:

  1. The test set should be random. That means every time we run your function, it should return a different test set. 
  2. For p = 0.25, the test data output should have 8 rows. Check with nrow(output)


```{r}
mtcars <- mtcars # Don't change this line
set.seed(1) # Don't change this line

test_split <- function(data, p){
  obs = nrow(data)
  
  test_set <- data[sample(obs, p*obs), ]
  return(test_set)
}

test_split(mtcars, .25)[1,]
test_split(mtcars, .25)

```


## 6. Creating Train & Test Data

Create a function that returns a vector of numbers that can be used to split a data into train AND test data

Inputs:

  1. Dataframe or matrix
  2. p parameter that specifies the proportion of the data considered the test set. This should be a number between 0 and 1. p=.5 means that 50% of the data will be considered the test set

Output:

  1. A vector of indicies that can be used to split a dataframe into train and test
    Example: c(5,1,21,56,12,13)

Notes:

  1. The indicies should be random. Everytime you run, it should produce a different result.
  2. For p = 0.25, the output vector should have 8 numbers. Check with length(output)

```{r}
mtcars <- mtcars # Don't change this line
set.seed(1) # Don't change this line

# This function creates a test split of data
train_test_split <- function(data, p){
  # Assigns the number of rows to obs
  obs = nrow(data)
  
  # Take a sample from obs
  idx <- sample(obs, round(p*obs))
  return(idx)
}

# Run train_test split and assign to index_split
index_split <- train_test_split(mtcars, .25)
index_split

# Split data into train and test
train_data <- mtcars[-index_split, ]
test_data <- mtcars[index_split, ]


```

## 7. Looping predictions

Using the previous train_test_split() function, make regression predictions for multiple test sizes on the mtcars dataset. You should calculate the mean squared error of each prediction. Some helper code has been included.


Notes:

  1. Our Y of interest is mpg
  
  2. You'll want to loop through the different test_sizes and run lm() and predict() on each train and test split
  
  3. To calculate residuals, subtract your predictions from the actual data. 
  
  4. MSE is calculated as the mean of the squared residuals
  
  5. Make sure to print out the MSE at the end of each loop

```{r}

mtcars <- mtcars # Don't change this line
set.seed(1) # Don't change this line

test_sizes = c(.10, .25, .5) # Don't change this line


for(i in test_sizes){
  # Split the index of each dataset by the size
  # print("Splitting Data into Train and Test Sets")
  index_split <- train_test_split(mtcars, i)
  train_data <- mtcars[-index_split, ]
  test_data <- mtcars[index_split, ]
  
  # Fit and predict
  # print("Fitting and Predicting")
  model_fit <- lm(mpg ~ ., data = train_data)
  prediction <- predict(model_fit, test_data)
  
  # 
  mse <- mean((prediction - test_data$mpg)^2)
  print(paste("The MSE for test size of", i, " is", mse))
  
  
}

```